---
title: "TidyTemplate"
date: 2021-01-18
output: html_output
---

# TidyTuesday



```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)


library(tidyverse)
library(tidytuesdayR)
library(scales)
theme_set(theme_light())
library(glue)
```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2021-01-05")
transit_cost<-tt$transit_cost %>%
        filter(!is.na(e)) %>%
        mutate_at(vars(start_year,end_year,real_cost), as.numeric) %>%
        mutate(country_code = ifelse(country == "UK","GB",country),
               country = countrycode(country_code,"iso2c","country.name"),
               tunnel_per = tunnel / length)
```
 

# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}
library(countrycode)
transit_cost %>%
        count(country,sort = TRUE)
  library(ggplot2)

#plotting the construction period of each line

transit_cost %>%
        filter(country == "United States") %>%
        mutate(line = fct_reorder(line,year)) %>%
        ggplot(aes(xmin = start_year, xmax = end_year, y = line,color = city, size = real_cost)) +
        geom_errorbarh(height = .1)+
        labs(x = "Year", y = "", color = "City", size =  "Real Cost")

transit_cost %>%
        ggplot(aes(cost_km_millions))+
        geom_histogram()+
        scale_x_continuous(label = dollar)+
        labs(x = "Cost/KM (Millions of USD)")

transit_cost %>%
        mutate(country = fct_lump(country,8), country = fct_reorder(country,cost_km_millions,na.rm = TRUE)) %>%
        ggplot(aes(cost_km_millions,country))+
        geom_boxplot()+
        scale_x_continuous(label = dollar)+
        labs(x = "Cost/KM (Millions of USD)")
        
```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}



```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}


  
``` 

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = "My TidyTuesday Plot.png",
  device = "png")

```
